Recursive algorithms, branching coefficients and applications

### 2010-11-04 AffineLieAlgebras/InformalNotes/article.tex
Figures annotations are improved.

\newtheorem{statement}{Statement}
\theoremstyle{definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

@@

Let $\frak{a}\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
Applying the Weyl-Kac character formula to the branching rule $\pi _{\frak{a}%
}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu
)}ch\left( L_{\frak{a}}^{\nu }\right) $ we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \frak{a}%
\right) }^{\left( \nu \right) }$ :
\begin{eqnarray}
\pi _{\frak{a}}\left( \frac{\sum_{\omega \in W}\epsilon (\omega )e^{\omega
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{\omega \in W_{\frak{a}}}\epsilon (\omega )e^{\omega (\nu +\rho _{%
\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\frak{a}}(\beta )}},  \label{eq:4} \\
\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}{R_{\frak{a}}}.
\end{eqnarray}
where according to our notations $\Delta _{\frak{a}}^{+}$ is the set of
positive roots of the subalgebra $\frak{a}$ (it is convenient to choose them
from the positive root subspace of $\frak{g}$). Consider the root space $%
\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to $\Delta _{\frak{a}}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
}^{\ast }|\forall \alpha \in \Delta _{\frak{a}};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\frak{a}}$,
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\frak{a}};\alpha \bot \beta \right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\frak{a}}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $\omega _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
_{\perp }}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall \alpha \in \Delta _{\frak{a}}\cup \Delta _{\frak{a}_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}

@@

\begin{remark}
This relation is a kind of a generalization of the Weyl formula for singular
element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\frak{a}}\left(
u\right) $ play the role of singular weights while the determinants $%
\epsilon (u)$ are changed for $\epsilon (u)\mathrm{\dim }\left( L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
u\right) }\right) .$ In fact when $\frak{a=g}$ both $\frak{a}_{\perp }$ and $%
\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
easily reobtained.
\end{remark}
Now we can state the main theorem which gives us the instrument for the
recurrent computation of the branching coefficients.
\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}

 As we have mentioned above (see (\ref{eq:21}) and (\ref
{eq:21-1})) when $\zeta \in \bar{C}_{\frak{a}}$ the coefficients $k_{\zeta
}^{(\mu )}$ coinside with the branching coefficients thus the
equation for $k_{\zeta }^{(\mu )}$ serve as recurrent relations for branching coefficients.
\begin{proof}
To proof the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
\frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}$ ,
\begin{eqnarray*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right)  &=&\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
}^{+}}\left( 1-e^{-\pi _{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
\mathrm{mult}_{\frak{a}}(\pi _{\frak{a}}\alpha )}\left( \sum_{\nu \in P_{%
\frak{a}}^{+}}b_{\nu }^{(\mu )}\sum_{\omega \in W_{\frak{a}}}\epsilon
(\omega )e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}}}\right) = \\
&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma )e^{-\gamma
}\left( \sum_{\nu \in P_{\frak{a}}^{+},\omega \in W_{\frak{a}}}\epsilon
(\omega )b_{\nu }^{(\mu )}e^{\omega (\nu +\rho _{\frak{a}})-\rho _{\frak{a}%
}}\right).
\end{eqnarray*}
Then decompose the last sum (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right) =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in the Lemma (in the left-hand side),
\begin{eqnarray*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right)  &=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\frak{a}_{\perp }}%
}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
\frak{a}_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma },
\end{eqnarray*}
Equate the coefficients of exponents in the last equality to get the following result:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu
_{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\frak{a}}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\frak{a}%
\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\frak{a}}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\frak{a}\subset \frak{g}}$ are not independent, they
are subject to the linear relations and the form of these relations changes
when the tested weight $\xi $ coinsides with one of \ the ''anomalous
weights'', $\left\{ \pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \frak{g}}$ and pass to the summation over the vectors of the
injection fan $\Gamma _{\frak{a}\subset \frak{g}}$ (see the definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}
\end{theorem}
\subsection{Embeddings and orthogonal pairs in simple Lie algebras}

@@

When both $\frak{g}$ and $\frak{a}$ are finite-dimensional all the regular
embeddings can be obtained by a successive elimination of nodes in the
extended Dynkin diagram of $\frak{g}$ (and $\Delta _{\bot }^{+}=\emptyset $
if $\frak{a}$ is maximal). For the classical series $A$, $C$ and $D$ when
the regular injection $\frak{a}\rightarrow \frak{g}$ is thus fixed, the
Dynkin diagram for $\frak{a}_{\bot }$ is obtained from the extended diagram
of $\frak{g}$ by eliminating the subdiagram of $\frak{a}$ and the adjacent
nodes:
\begin{table}[tbh]
\label{tab:diagrams} \noindent \centering{\
\begin{tabular}{|l|l|l|l|}
\hline
$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
\frak{a},\; \frak{a}_{\bot}$ &  \\ \hline
$A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps}
&  \\ \hline
$B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps}
&  \\ \hline
$C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps}
&  \\ \hline
$D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps}
&  \\ \hline
\end{tabular}
}
\caption{Subalgebras $\frak{a},\;\frak{a}_{\bot }$ for the classical series}
\end{table}
(drop the case B)

@@

\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ \omega (\mu +\rho
)-\rho ;\;\omega \in W\right\} $ of the anomalous weights for the $\frak{g}$%
-module $L^{(\mu )}$.

@@

%%    Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.

@@

%%          \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
%%          {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\

@@

%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}

@@

%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
%%          e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}

@@

%%        \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
%%          e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}

@@

%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\

@@

%%        \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.

@@

%%      Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in
%%      W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$
%%      such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,

@@

%%          \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}

@@

%%          = \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)
%%            \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}

@@

%%      Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and
%%      $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$,

@@

%%        \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
%%        (\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
%%        +\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho,

@@

%%        \fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
%%          e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}

@@

%%        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}

@@

%%            (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})

>>>>

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

@@

Let $\frak{a}\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
Applying the Weyl-Kac character formula to the branching rule $\pi _{\frak{a}%
}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu
)}ch\left( L_{\frak{a}}^{\nu }\right) $ we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \frak{a}%
\right) }^{\left( \nu \right) }$ :
\begin{eqnarray}
\pi _{\frak{a}}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\frak{a}}(\beta )}},  \label{eq:4} \\
\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}{R_{\frak{a}}}.
\end{eqnarray}
where according to our notations $\Delta _{\frak{a}}^{+}$ is the set of
positive roots of the subalgebra $\frak{a}$ (it is convenient to choose them
from the positive root subspace of $\frak{g}$). Consider the root space $%
\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to $\Delta _{\frak{a}}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
}^{\ast }|\forall \alpha \in \Delta _{\frak{a}};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\frak{a}}$,
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\frak{a}};\alpha \bot \beta \right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\frak{a}}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
_{\perp }}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall \alpha \in \Delta _{\frak{a}}\cup \Delta _{\frak{a}_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}

@@

\begin{remark}
This relation is a kind of a generalization of the Weyl formula for singular
element $\Psi _{\frak{g}}^{\mu }$ : the vectors $\mu _{\frak{a}}\left(
u\right) $ play the role of singular weights while the determinants $%
\epsilon (u)$ are changed for $\epsilon (u)\mathrm{\dim }\left( L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
u\right) }\right) .$ In fact when $\frak{a=g}$ both $\frak{a}_{\perp }$ and $%
\frak{h}_{\perp }$ are trivial, $U=W$ , and\ the original Weyl formula is
easily reobtained.
\end{remark}
Now we can state the main theorem which gives us the instrument for the
recurrent computation of the branching coefficients.
\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}

 As we have mentioned above (see (\ref{eq:21}) and (\ref
{eq:21-1})) when $\zeta \in \bar{C}_{\frak{a}}$ the coefficients $k_{\zeta
}^{(\mu )}$ coinside with the branching coefficients thus the
equation for $k_{\zeta }^{(\mu )}$ serve as recurrent relations for branching coefficients.
\begin{proof}
To prove the theorem return to the relation (\ref{eq:4}) and rewrite it for the element $\quad
\frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}$ ,
\begin{eqnarray*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right)  &=&\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot
}^{+}}\left( 1-e^{-\pi _{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-%
\mathrm{mult}_{\frak{a}}(\pi _{\frak{a}}\alpha )}\left( \sum_{\nu \in P_{%
\frak{a}}^{+}}b_{\nu }^{(\mu )}\sum_{w \in W_{\frak{a}}}\epsilon
(w )e^{w (\nu +\rho _{\frak{a}})-\rho _{\frak{a}}}\right) = \\
&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma )e^{-\gamma
}\left( \sum_{\nu \in P_{\frak{a}}^{+},w \in W_{\frak{a}}}\epsilon
(w )b_{\nu }^{(\mu )}e^{w (\nu +\rho _{\frak{a}})-\rho _{\frak{a}%
}}\right).
\end{eqnarray*}
Then decompose the last sum (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right) =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in the Lemma (in the left-hand side),
\begin{eqnarray*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right)  &=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\frak{a}_{\perp }}%
}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
\frak{a}_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{%
\frak{a}}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma },
\end{eqnarray*}
Equate the coefficients of exponents in the last equality to get the following result:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu
_{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\frak{a}}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\frak{a}%
\subset \frak{g}}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\frak{a}}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\frak{a}\subset \frak{g}}$ are not independent, they
are subject to the linear relations and the form of these relations changes
when the tested weight $\xi $ coinsides with one of \ the ''anomalous
weights'', $\left\{ \pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \frak{g}}$ and pass to the summation over the vectors of the
injection fan $\Gamma _{\frak{a}\subset \frak{g}}$ (see the definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}
\end{theorem}
\subsection{Embeddings and orthogonal pairs in simple Lie algebras}

@@

When both $\frak{g}$ and $\frak{a}$ are finite-dimensional all the regular
embeddings can be obtained by a successive elimination of nodes in the
extended Dynkin diagram of $\frak{g}$ (and $\Delta _{\bot }^{+}=\emptyset $
if $\frak{a}$ is maximal). For the classical series $A$, $C$ and $D$ when
the regular injection $\frak{a}\rightarrow \frak{g}$ is thus fixed, the
Dynkin diagram for $\frak{a}_{\bot }$ is obtained from the extended diagram
of $\frak{g}$ by eliminating the subdiagram of $\frak{a}$ and the adjacent
nodes:
\begin{table}[tbh]
\label{tab:diagrams} \noindent \centering{\
\begin{tabular}{|l|l|l|l|}
\hline
$\frak{g}$ & Extended diagram of $\frak{g}$ & Diagrams of the subalgebras $%
\frak{a},\; \frak{a}_{\bot}$ &  \\ \hline
$A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps}
&  \\ \hline
$C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps}
&  \\ \hline
$D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps}
&  \\ \hline
\end{tabular}
}
\caption{Subalgebras $\frak{a},\;\frak{a}_{\bot }$ for the classical series}
\end{table}

@@

\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
)-\rho ;\;w \in W\right\} $ of the anomalous weights for the $\frak{g}$%
-module $L^{(\mu )}$.

@@

%%    Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $w_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.

@@

%%          \sum_{w\in W_{\bot}\backslash W} \epsilon(w)\;
%%          {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
%%          \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(w(\mu+\rho)-\rho)}+ \right.\\

@@

%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}

@@

%%        \frac{\sum_{w\in W_{\mathfrak{a}}}\epsilon(w)
%%          e^{w(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}

@@

%%        \frac{\sum_{w\in W_{\bot}} \epsilon(w)
%%          e^{w(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}

@@

%%        \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\

@@

%%        \frac{\sum_{w\in W_{\mathfrak{a}}}\epsilon(w)e^{w(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.

@@

%%      Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{w}\in
%%      W_{\bot}\backslash W$ choose the representative $w \in \tilde{w}$
%%      such that $\pi_{\mathfrak{a}_{\bot}}w(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,

@@

%%          \fl \pi_{\mathfrak{a}}\left(\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}

@@

%%          = \pi_{\mathfrak{a}}\left(\sum_{w\in W_{\bot}\backslash W} \epsilon(w)
%%            \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot w(\mu+\rho)-\rho}}

@@

%%      Since $\nu\cdot \pi_{\mathfrak{a}}(w(\mu+\rho))=\pi_{\mathfrak{a}}(w(\mu+\rho))$ and
%%      $w(\mu+\rho)-\pi_{\mathfrak{a}}(w(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))$,

@@

%%        \nu\cdotw(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}
%%        (w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}
%%        +\pi_{\mathfrak{a}}(w(\mu+\rho))\bigr)-\rho,

@@

%%        \fl  \sum_{w\in W_{\bot}\backslash W} \epsilon(w) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu)
%%          e^{\nu \cdot w(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}

@@

%%        \sum_{w\in W_{\bot}\backslash W} \epsilon(w) e^{\pi_{\mathfrak{a}}(w(\mu+\rho))-\rho}

@@

%%            (\pi_{\mathfrak{a}_{\bot}}(w(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})
